\chapter{Introduction}

This project aims to develop an online self-sufficient educational platform which can be used to tutor students in writing a compiler. The project will provide the students with a roadmap for the development process and guide them along the roadmap with supporting documentation. Using the step-by-step guidance offered by the roadmap, the students will be able to build the compiler under minimal expert supervision.
\\
\\
We have designed the platform assuming that a student before starting to follow the roadmap has a basic knowledge of Data structures, Computer organization and a working proficiency in the C programming language. Being instructional in nature, this project gives the learner an insight into the working of LEX, YACC and the usage of these tools to develop a compiler for SIL (Simple Integer language). The theory involved would be learned on a \textit{need-to-do} basis. This, in our opinion would further enhance the understanding of the theory behind the implementation process.
\\
\\
An \textit{in-depth} explanation approach of the compiler design concepts and how these are interlinked with the back-end working of the compiler-generation tools has been used throughout the documentation. We believe that this would enable the students to have a better comprehension of the construction process and the convoluted nature of the different stages of construction. 
\\
\\
The primary focus of the project is to make the compiler construction process an easier task than it currently is now at the laboratory and to provide a strong foundation of basic knowledge in compiler development which would be useful in other areas of software engineering as well.
              